Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
revised contributions

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is non-trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach
(the increase in speed over a conventional one-stage verification 
approach is in most cases of several orders of magnitude).

>>>>

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is non-trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach 
yielding, in most cases,  a speed-up  
of several orders of magnitude over 
a conventional one-stage verification 
approach.
